A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-09-20 journal/experiments.tex
small add

  Applying the mutation-repair based approach is relatively easy here.  We used the {\bf universalmutator} tool \cite{RegExpMut} to generate 18,489 mutants for fuzzgoat.  This tool is far more aggressive than Andrews' tool, in terms of operators used, and is more widely available to typical users.  Of these 6,809 mutants actually compile, and trivial compiler equivalance \cite{TCE} can further reduce the set to 2,899 mutants to be used in producing repair bitvectors.  Computing the full bitvector set and all distances for the 38 crashes required just over 10 minutes.  While compiling and running mutants is a serious computational burden in the setting of a production compiler, it is negligible compared to the time required for fuzzing, in a typical fuzzing session, we suspect, even without using such simple additional reductions as checking the mutants for code covered by some crashing input.  This is partly because the number of mutants to consider is smaller, and partly because compiling GCC or SpiderMonkey is simply much slower than compiling more typical small-to-medium-sized fuzzing targets.  Fuzzing a very complex target, such as a database (e.g., LevelDB or RocksDB) might be more like compiler fuzzing, however.  Input runtime is also smaller for most non-compiler targets, we suspect.

>>>>

  Applying the mutation-repair based approach is relatively easy here.  We used the universalmutator tool \cite{RegExpMut} (\url{ https://github.com/agroce/universalmutator}) to generate 18,489 mutants for fuzzgoat.  This tool is far more aggressive than Andrews' tool, in terms of operators used, and, more importantly is more widely available to typical users and easy to apply to source code in a large set of languages, unlike, e.g., Proteum.  Of these mutants, only 6,809 actually compile, and trivial compiler equivalance \cite{TCE} can further reduce the set to 2,899 mutants to be used in producing repair bitvectors.  Computing the full bitvector set and all distances for the 38 crashes required just over 10 minutes.  While compiling and running mutants is a serious computational burden in the setting of a production compiler, it is negligible compared to the time required for fuzzing, in a typical fuzzing effort, we suspect, even without using such simple additional reductions as checking the mutants for code covered by some crashing input.  This is partly because the number of mutants to consider is smaller, and partly because compiling GCC or SpiderMonkey is simply much slower than compiling more typical small-to-medium-sized fuzzing targets.  Fuzzing a very complex target, such as a complex production-grade database (e.g., LevelDB or RocksDB) or the Linux kernel itself might be more like compiler fuzzing, however, in terms of mutation analysis cost.  Input runtime is also smaller for most non-compiler targets, we suspect, even including ``hard'' targets like databases and kernels.
